\LARGE \bf Stochastic Uncertainty Propagation in Power System Dynamics using Measure-valued Proximal Recursions

### 2021-07-05 Papers/Stochastic_Uncertainty_Propagation_TPS/JKO_Power_Systems_TPS.tex
updating Sec. V

%Suppose we denote the collection of generator buses in an \emph{unreduced} power system as $\mathcal{G}$, and the collection of non-generator buses as $\mathcal{N}$. 
Suppose that the \emph{unreduced} power network has $n$ generators and $m$ buses. Then the unreduced admittance matrix $\bm{Y}_{\rm{unreduced}}\in \mathbb{C}^{(n+m)\times(n+m)}$ can be partitioned as
\begin{align}
\bm{Y}_{\rm{unreduced}} = \begin{bmatrix} 
\begin{array}{c|c}
\bm{Y}_{\rm{bnd}} & \bm{Y}_{\rm{bnd{\text{-}}int}} \\
\hline\vspace*{-0.12in}\\
\bm{Y}_{\rm{bnd{\text{-}}int}}^{\top} & \bm{Y}_{\rm{int}}
\end{array}	
 \end{bmatrix},
\label{PartionedAdmittanceMatrix}	
\end{align} 
where $\bm{Y}_{\rm{bnd}}\in\mathbb{C}^{n\times n}$, $\bm{Y}_{\rm{int}}\in\mathbb{C}^{m\times m}$, $\bm{Y}_{\rm{bnd{\text{-}}int}}\in\mathbb{C}^{n\times m}$. The matrix \eqref{PartionedAdmittanceMatrix} relates the unreduced current vector $I_{\rm{unreduced}}\in\mathbb{C}^{n+m}$ with the unreduced voltage vector $E_{\rm{unreduced}}\in\mathbb{C}^{n+m}$ via the Kirchhoff equations
\begin{align}
I_{\rm{unreduced}} = \bm{Y}_{\rm{unreduced}} E_{\rm{unreduced}},
\label{DefUnreducedY}	
\end{align}
or equivalently, via its partitioned version associated with the interior and the boundary nodes:
\begin{align}
\begin{array}{c}
\begin{bmatrix}
I_{\rm{bnd}}\\
I_{\rm{int}} 	
\end{bmatrix}	
\end{array} = \bm{Y}_{\rm{unreduced}} \begin{array}{c}
\begin{bmatrix}
E_{\rm{bnd}}\\
E_{\rm{int}} 	
\end{bmatrix}	
\end{array}.
\label{PartitionedKirchoffEquation}	
\end{align}
%The reduced admittance matrix
%\begin{eqnarray}
%\bm{Y} &=& Y_{\mathcal{G}\mathcal{G}} - Y_{\mathcal{G}\mathcal{L}} Y_{\mathcal{L}\mathcal{L}}^{-1} Y_{\mathcal{L}\mathcal{G}} \\
%I_{red} &=& Y_{\mathcal{G}\mathcal{L}}Y_{\mathcal{L}\mathcal{L}}^{-1} I
%\end{eqnarray}

@@

\section{Numerical Simulations}\label{sec:NumericalSimulations}

\subsection{IEEE Test System}\label{subsec:NumSimIEEEBus}

>>>>

%Suppose we denote the collection of generator buses in an \emph{unreduced} power system as $\mathcal{G}$, and the collection of non-generator buses as $\mathcal{N}$. 
Suppose that the \emph{unreduced} power network has $n$ generators and $m$ buses. Then the unreduced admittance matrix $\bm{Y}_{\rm{unreduced}}\in \mathbb{C}^{(n+m)\times(n+m)}$ can be partitioned as
\begin{align}
\bm{Y}_{\rm{unreduced}} = \begin{bmatrix} 
\begin{array}{c|c}
\bm{Y}_{\rm{bnd}} & \bm{Y}_{\rm{bnd{\text{-}}int}} \\
\hline\vspace*{-0.12in}\\
\bm{Y}_{\rm{bnd{\text{-}}int}}^{\top} & \bm{Y}_{\rm{int}}
\end{array}	
 \end{bmatrix},
\label{PartionedAdmittanceMatrix}	
\end{align} 
where $\bm{Y}_{\rm{bnd}}\in\mathbb{C}^{n\times n}$, $\bm{Y}_{\rm{int}}\in\mathbb{C}^{m\times m}$, $\bm{Y}_{\rm{bnd{\text{-}}int}}\in\mathbb{C}^{n\times m}$. The matrix \eqref{PartionedAdmittanceMatrix} relates the unreduced current vector $I_{\rm{unreduced}}\in\mathbb{C}^{n+m}$ with the unreduced voltage vector $E_{\rm{unreduced}}\in\mathbb{C}^{n+m}$ via the Kirchhoff equations
\begin{align}
I_{\rm{unreduced}} = \bm{Y}_{\rm{unreduced}} E_{\rm{unreduced}},
\label{DefUnreducedY}	
\end{align}
or equivalently, via its partitioned version associated with the interior and the boundary nodes:
\begin{align}
\begin{array}{c}
\begin{bmatrix}
I_{\rm{bnd}}\\
I_{\rm{int}} 	
\end{bmatrix}	
\end{array} = \bm{Y}_{\rm{unreduced}} \begin{array}{c}
\begin{bmatrix}
E_{\rm{bnd}}\\
E_{\rm{int}} 	
\end{bmatrix}	
\end{array},
\label{PartitionedKirchoffEquation}	
\end{align}
where $I_{\rm{bnd}},E_{\rm{bnd}}\in\mathbb{C}^{n}$ and $I_{\rm{int}},E_{\rm{int}}\in\mathbb{C}^{m}$.
%The reduced admittance matrix
%\begin{eqnarray}
%\bm{Y} &=& Y_{\mathcal{G}\mathcal{G}} - Y_{\mathcal{G}\mathcal{L}} Y_{\mathcal{L}\mathcal{L}}^{-1} Y_{\mathcal{L}\mathcal{G}} \\
%I_{red} &=& Y_{\mathcal{G}\mathcal{L}}Y_{\mathcal{L}\mathcal{L}}^{-1} I
%\end{eqnarray}

@@

\section{Numerical Simulations}\label{sec:NumericalSimulations}
To illustrate the proposed computational framework, we next provide two numerical simulation case studies. In Sec. \ref{subsec:NumSimIEEEBus}, we consider the prediction of stochastic states for the IEEE 14 bus system--our main objective being to highlight the .

\subsection{IEEE 14 Bus System}\label{subsec:NumSimIEEEBus}
